CA of Music Genre Stereotypes

### 2025-06-20 analysis-bb-new.qmd
newer plots

```{r Creating individual matrices}
   make.mat <- function(x) {
      x <- matrix(as.numeric(x), 20, 15, byrow = TRUE)
      return(x)
      }
   bb.sdsm <- function(x) {
     tryCatch({
         w <- sdsm(x, alpha = 0.35, narrative = FALSE)
         return(w)
            }, error = function(e) {return(NULL)})
      }
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .9 | den < 0.1)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, make.mat) # creating individual two mode network of genre by labels
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   ind.mat.t <- lapply(ind.mat, function(x) {t(x)})
   ind.row <- lapply(ind.mat, function(x) {x %*% t(x)}) # individual genre projection
   ind.col <- lapply(ind.mat, function(x) {t(x) %*% x}) # individual label projection
   #row.bb <- lapply(ind.mat, bb.sdsm)
   #col.bb <- lapply(ind.mat.t, bb.sdsm)
   #null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
   #null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
   #row.bb <- row.bb[-null.rows]
   #col.bb <- col.bb[-null.cols]
   #save(row.bb, col.bb, file = "bb.RData")
   load(here("bb.RData"))
   row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(col.bb), ncol = 15, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- r # naming genre stacked matrix columns
   colnames(col.stack) <- c # naming label stacked matrix columns
   m <- nrow(row.stack)/20
   rownames(row.stack) <- rep(r, m) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, m) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
```

>>>>

```{r Creating individual matrices}
   make.mat <- function(x) {
      x <- matrix(as.numeric(x), 20, 15, byrow = TRUE)
      return(x)
      }
   bb.sdsm <- function(x) {
     tryCatch({
         w <- round(sdsm(x, alpha = NULL, missing.as.zero = TRUE)$Pupper, 2)
         return(w)
            }, error = function(e) {return(NULL)})
         }
   den <- rowSums(dat[,2:301])/300
   bad.den <- which(den > .9 | den < 0.1)
   dat2 <- dat[-c(bad.den), 2:301]
   ind.list <- split(dat2, seq(nrow(dat2))) # splitting each row of data frame into list objects
   ind.mat <- lapply(ind.list, make.mat) # creating individual two mode network of genre by labels
   ind.mat <- lapply(ind.mat, function(x) {rownames(x) <- r; x}) # naming individual rows
   ind.mat <- lapply(ind.mat, function(x) {colnames(x) <- c; x}) # naming individual columns
   names(ind.mat) <- dat$id_char[-c(bad.den)]
   ind.mat.t <- lapply(ind.mat, function(x) {t(x)})
   ind.row <- lapply(ind.mat, function(x) {x %*% t(x)}) # individual genre projection
   ind.col <- lapply(ind.mat, function(x) {t(x) %*% x}) # individual label projection
   # row.bb <- lapply(ind.mat, bb.sdsm)
   # col.bb <- lapply(ind.mat.t, bb.sdsm)
   # null.rows <- which(as.numeric(unlist(lapply(row.bb, is.null))) == 1)
   # null.cols <- which(as.numeric(unlist(lapply(col.bb, is.null))) == 1)
   # row.bb <- row.bb[-null.rows]
   # col.bb <- col.bb[-null.cols]
   # row.bb <- lapply(row.bb, function(x) {ifelse(is.nan(x), 1, x)})
   # col.bb <- lapply(col.bb, function(x) {ifelse(is.nan(x), 1, x)})
   # row.bb <- lapply(row.bb, function(x) {diag(x) <- 1; x})
   # col.bb <- lapply(col.bb, function(x) {diag(x) <- 1; x})
   # save(row.bb, col.bb, file = here("bb.RData"))
   load(here("bb.RData"))
   row.bb <- lapply(row.bb, function(x) {(x < 0.45) * 1})
   col.bb <- lapply(col.bb, function(x) {(x < 0.45) * 1})
   row.stack <- matrix(unlist(row.bb), ncol = 20, byrow = TRUE) # genre stacked matrix
   col.stack <- matrix(unlist(col.bb), ncol = 15, byrow = TRUE) # label stacked matrix
   colnames(row.stack) <- r # naming genre stacked matrix columns
   colnames(col.stack) <- c # naming label stacked matrix columns
   m <- nrow(row.stack)/20
   rownames(row.stack) <- rep(r, m) # naming genre stacked matrix rows
   rownames(col.stack) <- rep(c, m) # naming label stacked matrix rows
   zero.rows.r <- which(rowSums(row.stack) == 0) # which genre stacked matrix rows sum to zero?
   zero.rows.c <- which(rowSums(col.stack) == 0) # which label stacked matrix rows sum to zero?
```
